TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
More

\section{Abstraction}\label{sec:synthesis}
One of the major weakness of the previous version of \tactictoe is that
it could not create its own tactics. Indeed, sometimes no previous tactic is
adapted for a certain goal and creating a new tactic is necessary.
%Experiments in section, show how different degrees of tactic synthesis could
%improve the success rate of \tactictoe.
We present a way to create tactics with different arguments
by abstracting them and re-instantiating them using a predictor for that kind
of argument. In the spirit of the orthogonalization method, we will try to
create tactics that are more general but have the same effect as the
ungeneralized one. The generalized tactics are typically slower that their 
counterpart, but the added flexibility is worthwhile in practice. Moreover, 
since we impose a timeout on each tactic (0.05 seconds by default), very slow 
tactics fails and thus are not selected.

>>>>

\section{Abstraction}\label{sec:synthesis}
One of the major weakness of the previous version of \tactictoe was that
it could not create its own tactics. Indeed, sometimes no previous tactic is
adapted for a certain goal and creating a new tactic is necessary.
%Experiments in section, show how different degrees of tactic synthesis could
%improve the success rate of \tactictoe.
In this section we present a way to create tactics with different arguments
by abstracting them and re-instantiating them using a predictor for that kind
of argument. In the spirit of the orthogonalization method, we will try to
create tactics that are more general but have the same effect as the
ungeneralized one. The generalized tactics are typically slower that their 
original variants, but the added flexibility is worthwhile in practice. Moreover, 
since we impose a timeout on each tactic (0.05 seconds by default), very slow 
tactics fail and thus are not selected.
